Structured Versus Decorated Cospans

### 2020-11-18 cospans.tex
More work on Theorem 2.2

Next, we define the four structure functors $U,S,T$ and $\odot$. The unit functor $U \maps F\lCsp_0 \to F\lCsp_1$ is defined on objects as: 
\begin{equation}\label{eq:UFCsp}
\begin{tikzpicture}[scale=1.5]
\node (E) at (-1,0) {$a$};
\node (F) at (-.5,0) {$\mapsto$};
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$a$};
\node (C) at (2,0) {$a$};
\node (D) at (3,0) {$!_a \in F(a)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$1$} (B)
(C) edge node[above]{$1$} (B);
\end{tikzpicture}
\end{equation}
where $!_a \in F(a)$ is the \define{trivial decoration} on $a$ given by the composite of the unique map $F(!) \maps F(0) \to F(a)$ and the morphism $\phi \maps 1 \to F(0)$  which comes from $F \maps \A \to \Cat$ being lax monoidal.  For morphisms, the functor $U$ is defined as:
\[
\begin{tikzpicture}[scale=1.5]
\node (G) at (-1,0.5) {$a$};
\node (G') at (-1,-0.5) {$a'$};
\node (A) at (0,0.5) {$a$};
\node (A') at (0,-0.5) {$a'$};
\node (B) at (1,0.5) {$a$};
\node (C) at (2,0.5) {$a$};
\node (C') at (2,-0.5) {$a'$};
\node (D) at (1,-0.5) {$a'$};
\node (E) at (3,0.5) {$!_a \in F(a)$};
\node (F) at (3,-0.5) {$!_{a'} \in F(a')$};
\node (H) at (-0.5,0) {$\mapsto$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$1$} (B)
(C) edge node[above]{$1$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[right]{$f$} (C')
(A') edge node[above] {$1$} (D)
(C') edge node[above] {$1$} (D)
(B) edge node [left] {$f$} (D)
(G) edge node [left] {$f$} (G');
\end{tikzpicture}
\]
together with the morphism $\tau_{!_f} = F(f) F(!) \phi \maps 1 \to F(a')$. For the source and target functors $S, T \maps F\lCsp_1 \to F\lCsp_0$, given an object $F\lCsp_1$, which is an $F$-decorated cospan,
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$m$};
\node (C) at (2,0) {$b$};
\node (D) at (3,0) {$x \in F(m)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
the source is the object $a$ and the target is the object $b$. Given a morphism of $F\lCsp_1$, which is a map of $F$-decorated cospans,
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$a$};
\node (A') at (0,-0.5) {$a'$};
\node (B) at (1,0.5) {$m$};
\node (C) at (2,0.5) {$b$};
\node (C') at (2,-0.5) {$b'$};
\node (D) at (1,-0.5) {$m'$};
\node (E) at (3,0.5) {$x \in F(m)$};
\node (F) at (3,-0.5) {$x' \in F(m')$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[right]{$g$} (C')
(A') edge node[above] {$i'$} (D)
(C') edge node[above] {$o'$} (D)
(B) edge node [left] {$h$} (D);
\end{tikzpicture}
\]
$$\tau \maps F(h)(x) \to x'$$
the source is the morphism $f$ and the target is the morphism $g$. The three functors $S,T$ and $U$ satisfy the equations $SU=\id_{\A}=TU$.

@@

Lastly, our double category is required to have an associator $\alpha$ (\textbf{overusing alpha, ignoring for now}) and left and right unitors $\lambda$ and $\rho$ which are natural isomorphisms governing the composition of horizontal 1-cells that are required to satisfy the standard coherence axioms for a monoidal category, as well as $S(\alpha),S(\lambda),S(\rho),T(\alpha),T(\lambda)$ and $T(\rho)$ all being identities. We will only show the associator $\alpha$, left unitor $\lambda$ and the pentagon identity, as the remaining details will be similar to these.

@@

We next construct the left unitor. Given a horizontal 1-cell $M$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$m$};
\node (C) at (2,0) {$b$};
\node (D) at (3,0) {$x \in F(m)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
the left unitor will be a globular 2-morphism $\lambda \colon 1_a \odot M \to M$, where the identity horizontal 1-cell on the object $a$ will once again make use of the trivial decoration on an object introduced earlier.
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$a$};
\node (C) at (2,0) {$a$};
\node (D) at (3,0) {$!_a \in F(a)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\id_a$} (B)
(C) edge node[above]{$\id_a$} (B);
\end{tikzpicture}
\]
To compose $1_a$ and $M$, we first compose the two cospans in $\A$ by pushing out over their shared object $a$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$a$};
\node (C) at (2,0) {$a$};
\node (D) at (3,1) {$m$};
\node (E) at (4,0) {$b$};
\node (F) at (2,2) {$a+m$};
\node (G) at (2,3) {$a+_{a} m$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\id_a$} (B)
(C) edge node[above]{$\id_a$} (B)
(C) edge node [above] {$i$} (D)
(E) edge node [above] {$o$} (D)
(B) edge node [above] {$j_a$} (F)
(D) edge node [above] {$j_m$} (F)
(F) edge node [left] {$\psi$} (G)
(A) edge[bend left] node [left] {$\psi j_a$} (G)
(E) edge[bend right] node [right] {$\psi j_{m} o$} (G);
\end{tikzpicture}
\]
The composite decoration $!_a \odot x$ will be given by the composite
$$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{!_a \times x} F(a) \times F(m) \xrightarrow{\phi_{a,m}} F(a+m) \xrightarrow{F(\psi)} F(a+_{a} m).$$
The left unitor is then the map of $F$-decorated cospans determined by the following map of cospans in $\A$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$a$};
\node (A') at (0,-0.5) {$a$};
\node (B) at (1.5,0.5) {$a+_{a} m$};
\node (C) at (3,0.5) {$b$};
\node (C') at (3,-0.5) {$b$};
\node (D) at (1.5,-0.5) {$m$};
\node (E) at (4.5,0.5) {$!_a \odot x \in F(a+_{a} m)$};
\node (F) at (4.5,-0.5) {$x \in F(m)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\psi j_a$} (B)
(C) edge node[above]{$\psi j_m o$} (B)
(A) edge node[left]{$\id_{a}$} (A')
(C) edge node[right]{$\id_{b}$} (C')
(A') edge node [above]{$i$} (D)
(C') edge node [above]{$o$} (D)
(B) edge node [left] {$\ell$} (D);
\end{tikzpicture}
\]
together with the decoration morphism $\tau_\lambda \colon F(\ell)(!_a \odot x) \to x$; note, that $\ell \colon a+_a m \to m$ is a canonical isomorphism as both $a+_a m$ and $m$ are colimits of the span $a \xleftarrow{\id_a} a \xrightarrow{i} m$. The right unitor $\rho$ is similar, the two unitality squares are similar to the associator shown above, and it is clear that the source and target functors applied to the associator and left and right unitors yield identities.

@@

\begin{thm}\label{DC}
Let $\A$ be a category with chosen finite colimits and $F \maps \A \to \Cat$ a symmetric lax monoidal pseudofunctor. Then the double category $F\lCsp$ of Theorem \ref{thm:decorated_cospans} is symmetric monoidal.
\end{thm}
%!!!Kenny: We should try to make this proof shorter.
%Christina: Yes! Again, I think that it can be simplified and easier for the reader to follow. Should tackle after we do the previous theorem. Also notice that a big part of the following proof is commented out below. 
\begin{proof}
The definition of symmetric monoidal double category may be found in Definition \ref{defn:smdc}. We must show that both the category of objects $F\lCsp_0$ and the category of arrows $F\lCsp_1$ are symmetric monoidal categories, show that the monoidal unit of $F\lCsp_0$ is preserved by the unit functor $U$, show that the source and target functors $S,T \colon F\lCsp_1 \to F\lCsp_0$ are strict symmetric monoidal functors which preserve the associativity and unit constraints, define the globular isomorphisms $\chi$ and $\mu$ that relate how composition and units interact with the tensor product, and check that the required axioms are satisfied.

First we note that the category of objects $F\lCsp_0=\A$ is symmetric monoidal under chosen binary coproducts in $\A$ and the left and right unitors, associators and braidings are given as natural maps. Next we show that $F\lCsp_1$ is symmetric monoidal. The category of arrows $F\lCsp_1$ has:
\begin{enumerate}
\item{objects as $F$-decorated cospans, which are pairs:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$(a$};
\node (B) at (1,0) {$m$};
\node (C) at (2,0) {$b,$};
\node (D) at (2.6,0) {$x \in F(m))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
and}
\item{morphisms as maps of $F$-decorated cospans, which are cospans in $\A$
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$a$};
\node (A') at (0,-0.5) {$a'$};
\node (B) at (1,0.5) {$m$};
\node (C) at (2,0.5) {$b$};
\node (C') at (2,-0.5) {$b'$};
\node (D) at (1,-0.5) {$m'$};
\node (E) at (3,0.5) {$x \in F(m)$};
\node (F) at (3,-0.5) {$x' \in F(m')$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[right]{$g$} (C')
(A') edge node [above]{$i'$} (D)
(C') edge node [above]{$o'$} (D)
(B) edge node [left] {$h$} (D);
\end{tikzpicture}
\]
together with a decoration morphism $\tau \maps F(h)(x) \to x'$.
}
\end{enumerate}

First we define the tensor product and monoidal unit of $F\lCsp_1$. Given two objects $M_1$ and $M_2$ of $F\lCsp_1$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a_1$};
\node (B) at (1,0) {$m_1$};
\node (C) at (2,0) {$b_1$};
\node (D) at (1,-0.5) {$x_1 \in F(m_1)$};
\node (E) at (3,0) {$a_2$};
\node (F) at (4,0) {$m_2$};
\node (G) at (5,0) {$b_2$};
\node (H) at (4,-0.5) {$x_2 \in F(m_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i_1$} (B)
(C) edge node[above]{$o_1$} (B)
(E) edge node[above]{$i_2$} (F)
(G) edge node[above]{$o_2$} (F);
\end{tikzpicture}
\]
their tensor product $M_1 \otimes M_2$ is given by taking the coproducts of the cospans in $\A$
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a_1+a_2$};
\node (B) at (1.5,0) {$m_1+m_2$};
\node (C) at (3,0) {$b_1+b_2$};
\node (D) at (4.55,0) {$x_1+x_2 \in F(m_1+m_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i_1+i_2$} (B)
(C) edge node[above]{$o_1+o_2$} (B);
\end{tikzpicture}
\]
and where the decoration on the apex is obtained using the natural transformation of the symmetric lax monoidal pseudofunctor $F$: $$x_1+x_2 \mapseqq 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x_1 \times x_2} F(m_1) \times F(m_2) \xrightarrow{\phi_{m_1,m_2}} F(m_1+m_2).$$The monoidal unit $0_{F\lCsp_1}$ is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$0$};
\node (B) at (1,0) {$0$};
\node (C) at (2,0) {$0$};
\node (D) at (3,0) {$!_0 \in F(0)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$!$} (B)
(C) edge node[above]{$!$} (B);
\end{tikzpicture}
\]
where $0$ is the monoidal unit of $\A$ and $!_0 \maps 1 \to F(0)$ is the morphism which is part of the structure of the symmetric lax monoidal pseudofunctor $F \maps \A \to \Cat$. It is also clear that $U(0)=0_{F\lCsp_1}$, where $0_{F\lCsp_1}$ is the monoidal unit of $F\lCsp_1$.

@@

@@

together with the decoration isomorphism $\tau_{a,b} \maps !_{a+b} \xrightarrow{\sim} !_a + !_b$ given by the unique map between the two initial objects $!_{a+b}$ and $!_a + !_b$ in $F(a+b)$. For the former globular 2-morphism $\chi$, we first introduce some notation for objects $M_1,M_2,N_1$ and $N_2$ of $F\lCsp_1$:

>>>>

Next, we define the four structure functors $U,S,T$ and $\odot$. The unit functor $U \maps F\lCsp_0 \to F\lCsp_1$ is defined on objects as: 
\begin{equation}\label{eq:UFCsp}
\begin{tikzpicture}[scale=1.5]
\node (E) at (-1,0) {$a$};
\node (F) at (-.5,0) {$\mapsto$};
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$a$};
\node (C) at (2,0) {$a$};
\node (D) at (3,0) {$\bot_a \in F(a)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$1$} (B)
(C) edge node[above]{$1$} (B);
\end{tikzpicture}
\end{equation}
where $\bot_a \in F(a)$ is the \define{trivial decoration} on $a$ given by the composite of the unique map $F(!) \maps F(0) \to F(a)$ and the morphism $\phi \maps 1 \to F(0)$  which comes from $F \maps \A \to \Cat$ being lax monoidal.  For morphisms, the functor $U$ is defined as:
\[
\begin{tikzpicture}[scale=1.5]
\node (G) at (-1,0.5) {$a$};
\node (G') at (-1,-0.5) {$a'$};
\node (A) at (0,0.5) {$a$};
\node (A') at (0,-0.5) {$a'$};
\node (B) at (1,0.5) {$a$};
\node (C) at (2,0.5) {$a$};
\node (C') at (2,-0.5) {$a'$};
\node (D) at (1,-0.5) {$a'$};
\node (E) at (3,0.5) {$\bot_a \in F(a)$};
\node (F) at (3,-0.5) {$\bot_{a'} \in F(a')$};
\node (H) at (-0.5,0) {$\mapsto$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$1$} (B)
(C) edge node[above]{$1$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[right]{$f$} (C')
(A') edge node[above] {$1$} (D)
(C') edge node[above] {$1$} (D)
(B) edge node [left] {$f$} (D)
(G) edge node [left] {$f$} (G');
\end{tikzpicture}
\]
together with the morphism $\tau_{\bot_f} = F(f) F(!) \phi \maps 1 \to F(a')$. For the source and target functors $S, T \maps F\lCsp_1 \to F\lCsp_0$, given an object $F\lCsp_1$, which is an $F$-decorated cospan,
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$m$};
\node (C) at (2,0) {$b$};
\node (D) at (3,0) {$x \in F(m)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
the source is the object $a$ and the target is the object $b$. Given a morphism of $F\lCsp_1$, which is a map of $F$-decorated cospans,
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$a$};
\node (A') at (0,-0.5) {$a'$};
\node (B) at (1,0.5) {$m$};
\node (C) at (2,0.5) {$b$};
\node (C') at (2,-0.5) {$b'$};
\node (D) at (1,-0.5) {$m'$};
\node (E) at (3,0.5) {$x \in F(m)$};
\node (F) at (3,-0.5) {$x' \in F(m')$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[right]{$g$} (C')
(A') edge node[above] {$i'$} (D)
(C') edge node[above] {$o'$} (D)
(B) edge node [left] {$h$} (D);
\end{tikzpicture}
\]
$$\tau \maps F(h)(x) \to x'$$
the source is the morphism $f$ and the target is the morphism $g$. The three functors $S,T$ and $U$ satisfy the equations $SU=\id_{\A}=TU$.

@@

Lastly, our double category is required to have an associator $\alpha$ and left and right unitors $\lambda$ and $\rho$ which are natural isomorphisms governing the composition of horizontal 1-cells that are required to satisfy the standard coherence axioms for a monoidal category, as well as $S(\alpha),S(\lambda),S(\rho),T(\alpha),T(\lambda)$ and $T(\rho)$ all being identities. We will only show the associator $\alpha$, left unitor $\lambda$ and the pentagon identity, as the remaining details will be similar to these.

@@

We next construct the left unitor. Given a horizontal 1-cell $M$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$m$};
\node (C) at (2,0) {$b$};
\node (D) at (3,0) {$x \in F(m)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
the left unitor will be a globular 2-morphism $\lambda \colon 1_a \odot M \to M$, where the identity horizontal 1-cell on the object $a$ will once again make use of the trivial decoration on an object introduced earlier.
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$a$};
\node (C) at (2,0) {$a$};
\node (D) at (3,0) {$\bot_a \in F(a)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\id_a$} (B)
(C) edge node[above]{$\id_a$} (B);
\end{tikzpicture}
\]
To compose $1_a$ and $M$, we first compose the two cospans in $\A$ by pushing out over their shared object $a$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,1) {$a$};
\node (C) at (2,0) {$a$};
\node (D) at (3,1) {$m$};
\node (E) at (4,0) {$b$};
\node (F) at (2,2) {$a+m$};
\node (G) at (2,3) {$a+_{a} m$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\id_a$} (B)
(C) edge node[above]{$\id_a$} (B)
(C) edge node [above] {$i$} (D)
(E) edge node [above] {$o$} (D)
(B) edge node [above] {$j_a$} (F)
(D) edge node [above] {$j_m$} (F)
(F) edge node [left] {$\psi$} (G)
(A) edge[bend left] node [left] {$\psi j_a$} (G)
(E) edge[bend right] node [right] {$\psi j_{m} o$} (G);
\end{tikzpicture}
\]
The composite decoration $\bot_a \odot x$ will be given by the composite
$$1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{\bot_a \times x} F(a) \times F(m) \xrightarrow{\phi_{a,m}} F(a+m) \xrightarrow{F(\psi)} F(a+_{a} m).$$
The left unitor is then the map of $F$-decorated cospans determined by the following map of cospans in $\A$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$a$};
\node (A') at (0,-0.5) {$a$};
\node (B) at (1.5,0.5) {$a+_{a} m$};
\node (C) at (3,0.5) {$b$};
\node (C') at (3,-0.5) {$b$};
\node (D) at (1.5,-0.5) {$m$};
\node (E) at (4.5,0.5) {$\bot_a \odot x \in F(a+_{a} m)$};
\node (F) at (4.5,-0.5) {$x \in F(m)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\psi j_a$} (B)
(C) edge node[above]{$\psi j_m o$} (B)
(A) edge node[left]{$\id_{a}$} (A')
(C) edge node[right]{$\id_{b}$} (C')
(A') edge node [above]{$i$} (D)
(C') edge node [above]{$o$} (D)
(B) edge node [left] {$\ell$} (D);
\end{tikzpicture}
\]
together with the decoration morphism $\tau_\lambda \colon F(\ell)(\bot_a \odot x) \to x$; note, that $\ell \colon a+_a m \to m$ is a canonical isomorphism as both $a+_a m$ and $m$ are colimits of the span $a \xleftarrow{\id_a} a \xrightarrow{i} m$. The right unitor $\rho$ is similar, the two unitality squares are similar to the associator shown above, and it is clear that the source and target functors applied to the associator and left and right unitors yield identities.

@@

\begin{thm}\label{DC}
Let $\A$ be a category with chosen finite colimits and $F \maps \A \to \Cat$ a symmetric lax monoidal pseudofunctor. Then the double category $F\lCsp$ of Theorem \ref{thm:decorated_cospans} is symmetric monoidal, where
\item{the tensor product of two objects $a$ and $b$ is their chosen coproduct $a+b$ in $\A$,}
\item{the tensor product of two vertical 1-morphisms $f \colon a \to b$ and $f' \colon a' \to b'$ is the vertical 1-morphism $f+f' \colon a+a' \to b+b'$,}
\item{the tensor product of two horizontal 1-cells $M$ and $N$:
is the horizontal 1-cell $M \otimes N$:
\node (B) at (1.5,0) {$m_1+m_2$};
\node (D) at (4.55,0) {$x_1+x_2 \in F(m_1+m_2)$};
$$x_1+x_2 \mapseqq 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x_1 \times x_2} F(m_1) \times F(m_2) \xrightarrow{\phi_{m_1,m_2}} F(m_1+m_2)$$}
\item{the tensor product of two 2-morphisms $\alpha$ and $\beta$:
\node (G) at (4,0.5) {$c$};
\node (I) at (6,0.5) {$d$};
\node (G') at (4,-0.5) {$c'$};
\node (I') at (6,-0.5) {$d'$};
\node (L) at (1,-1) {$\tau_\alpha \maps F(h)(x) \to x'$};
\node (M) at (5,-1) {$\tau_\beta \maps F(h')(y) \to y'$};
(G) edge node [left] {$f'$} (G')
(H) edge node [left] {$h'$} (H')
(I) edge node [right] {$g'$} (I')
is the 2-morphism $\alpha \otimes \beta$:
\node (A) at (0,0.5) {$a+c$};
\node (A') at (0,-0.5) {$a'+c'$};
\node (B) at (2,0.5) {$m+n$};
\node (C) at (4,0.5) {$b+d$};
\node (C') at (4,-0.5) {$b'+d'$};
\node (D) at (2,-0.5) {$m'+n'$};
\node (E) at (5.5,0.5) {$x+y \in F(m+n)$};
\node (F) at (5.5,-0.5) {$x'+y' \in F(m'+n')$};
(C) edge node[above]{$o_1+o_2$} (B)
(A) edge node[left]{$f+f'$} (A')
(C) edge node[left]{$g+g'$} (C')
(A') edge node [above]{$i_1'+i_2'$} (D)
(C') edge node [above]{$o_1'+o_2'$} (D)
(B) edge node [left] {$h+h'$} (D);
$$\tau_{\alpha+\beta} \colon F(h+h')(x+y) \to x'+y'$$
where the decoration morphism $\tau_{\alpha+\beta}$ comes from the pasted diagram:
(B) edge node [right] {$F(h + h')$} (B')
(E) edge node [right] {$F(h) \times F(h')$} (E');
\end{thm}
%!!!Kenny: We should try to make this proof shorter.
%Christina: Yes! Again, I think that it can be simplified and easier for the reader to follow. Should tackle after we do the previous theorem. Also notice that a big part of the following proof is commented out below. 
\begin{proof}
The definition of symmetric monoidal double category may be found in Definition \ref{defn:smdc}. We must show that both the category of objects $F\lCsp_0$ and the category of arrows $F\lCsp_1$ are symmetric monoidal categories, show that the monoidal unit of $F\lCsp_0$ is preserved by the unit functor $U$, show that the source and target functors $S,T \colon F\lCsp_1 \to F\lCsp_0$ are strict symmetric monoidal functors which preserve the associativity and unit constraints, define the globular isomorphisms $\chi$ and $\mu$ that relate how composition and units interact with the tensor product, and check that the required axioms are satisfied.

First we note that the category of objects $F\lCsp_0=\A$ is symmetric monoidal under chosen binary coproducts in $\A$ and the left and right unitors, associators and braidings are given as natural maps. Next we show that $F\lCsp_1$ is symmetric monoidal. The category of arrows $F\lCsp_1$ has:
\begin{enumerate}
\item{objects as $F$-decorated cospans, which are pairs:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$(a$};
\node (B) at (1,0) {$m$};
\node (C) at (2,0) {$b,$};
\node (D) at (2.6,0) {$x \in F(m))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
and}
\item{morphisms as maps of $F$-decorated cospans, which are cospans in $\A$
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$a$};
\node (A') at (0,-0.5) {$a'$};
\node (B) at (1,0.5) {$m$};
\node (C) at (2,0.5) {$b$};
\node (C') at (2,-0.5) {$b'$};
\node (D) at (1,-0.5) {$m'$};
\node (E) at (3,0.5) {$x \in F(m)$};
\node (F) at (3,-0.5) {$x' \in F(m')$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[right]{$g$} (C')
(A') edge node [above]{$i'$} (D)
(C') edge node [above]{$o'$} (D)
(B) edge node [left] {$h$} (D);
\end{tikzpicture}
\]
together with a decoration morphism $\tau \maps F(h)(x) \to x'$.
}
\end{enumerate}
First we define the tensor product and monoidal unit of $F\lCsp_1$. Given two objects $M_1$ and $M_2$ of $F\lCsp_1$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a_1$};
\node (B) at (1,0) {$m_1$};
\node (C) at (2,0) {$b_1$};
\node (D) at (1,-0.5) {$x_1 \in F(m_1)$};
\node (E) at (3,0) {$a_2$};
\node (F) at (4,0) {$m_2$};
\node (G) at (5,0) {$b_2$};
\node (H) at (4,-0.5) {$x_2 \in F(m_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i_1$} (B)
(C) edge node[above]{$o_1$} (B)
(E) edge node[above]{$i_2$} (F)
(G) edge node[above]{$o_2$} (F);
\end{tikzpicture}
\]
their tensor product $M_1 \otimes M_2$ is given by taking the coproducts of the cospans in $\A$
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a_1+a_2$};
\node (B) at (1.5,0) {$m_1+m_2$};
\node (C) at (3,0) {$b_1+b_2$};
\node (D) at (4.55,0) {$x_1+x_2 \in F(m_1+m_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i_1+i_2$} (B)
(C) edge node[above]{$o_1+o_2$} (B);
\end{tikzpicture}
\]
where the decoration on the apex is obtained using the natural transformation of the symmetric lax monoidal pseudofunctor $F$: $$x_1+x_2 \mapseqq 1 \xrightarrow{\lambda^{-1}} 1 \times 1 \xrightarrow{x_1 \times x_2} F(m_1) \times F(m_2) \xrightarrow{\phi_{m_1,m_2}} F(m_1+m_2).$$The monoidal unit $0_{F\lCsp_1}$ is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$0$};
\node (B) at (1,0) {$0$};
\node (C) at (2,0) {$0$};
\node (D) at (3,0) {$\bot_0 = \phi \in F(0)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$!$} (B)
(C) edge node[above]{$!$} (B);
\end{tikzpicture}
\]
where $0$ is the monoidal unit of $\A$ and $\phi \maps 1 \to F(0)$ is the morphism which is part of the structure of the symmetric lax monoidal pseudofunctor $F \maps \A \to \Cat$. It is also clear that $U(0)=0_{F\lCsp_1}$.

@@

\node (E) at (5.5,0.5) {$\bot_{a+b} \in F(a+b)$};
\node (F) at (5.5,-0.5) {$\bot_a + \bot_b \in F(a+b)$};

@@

together with the decoration isomorphism $\tau_{a,b} \maps \bot_{a+b} \xrightarrow{\sim} \bot_a + \bot_b$ given by the unique map between the two initial objects $\bot_{a+b}$ and $\bot_a + \bot_b$ in $F(a+b)$. For the former globular 2-morphism $\chi$, we first introduce some notation for objects $M_1,M_2,N_1$ and $N_2$ of $F\lCsp_1$:
